IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/intro.tex
minor intro change
Space smithing
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

What distinguishes this setting from previous coarse-grained IFC
systems?
%
First, even though the underlying semantic model involves communicating
tasks, these tasks can be coordinated together in ways that simulate
traditional features in monolithic languages.  In fact, simulating
features in this way is a very useful \emph{design tool} for discovering
what variants of the features are permissible and which are not.
%
Second, although completely separate tasks are semantically easy to
reason about, real-world implementations often blur the lines between
tasks in the name of efficiency.
Characterizing what optimizations are permissible is subtle, since
removing transitions from the operational semantics of a language can
break non-interference.  We partially address this issue
by characterizing isomorphisms between the operational semantics of our
defined language and a concrete implementation, showing that if this
relationship holds, then non-interference in the abstract specification
carries over to the concrete implementation.

>>>>

There are a number of points that distinguish this setting from
previous coarse-grained IFC systems.
%
First, even though the underlying semantic model involves communicating
tasks, these tasks can be coordinated together in ways that simulate
features of traditional languages.
%
In fact, simulating
features in this way is a useful \emph{design tool} for discovering
what variants of the features are permissible and which are not.
%
Second, although completely separate tasks are semantically easy to
reason about, real-world implementations often blur the lines between
tasks in the name of efficiency.
Characterizing what optimizations are permissible is subtle, since
removing transitions from the operational semantics of a language can
break non-interference.  We partially address this issue
by characterizing isomorphisms between the operational semantics of our
abstract language and a concrete implementation, showing that if this
relationship holds, then non-interference in the abstract specification
carries over to the concrete implementation.
